Fifteen years of decentralization attempts

### 2014-03-22 paper.tex
changes to 4 and 5
with respect to last meeting!

	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor.

@@

\section{Current decentralized systems}
	\label{sec:decentralized}

	Many decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}. Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan. Each of these decentralized networks will be discussed in this section. Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority). Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.

>>>>

	Decentralizing systems comes with a variety of problems. The most important reason why one would decentralize are security and anonymity. When having a central authority this authority can be used for bootstrapping, key management and to manage the reputation of the users, but if one of these authorities were taken control of, security of the anonymity could be compromised. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor.

@@

\section{Decentralized privacy enhancing systems}
	\label{sec:decentralized}

	Many decentralized peer-to-peer networks have been proposed, yet only some have been implemented and are currently in use and still actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}. In this section, some popular peer-to-peer overlay networks are discussed. Most of these networks are used in practice and can be used to compare Tor with. Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority). Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.
